### 2020-10-12 README.Rmd
update pkgdown link

# infer R Package <img src="https://github.com/tidymodels/infer/blob/master/figs/infer_gnome.png?raw=true" align="right" width=125 />

@@

To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at <https://infer.netlify.com>.

@@

To install the experimental version of `infer` (do so at your own risk), make sure to install `remotes` first.

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("tidymodels/infer", ref = "develop")
```

To see documentation for the experimental version of `infer`, the `pkgdown` site is available at <https://infer-dev.netlify.com>.

@@

For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://rstd.io/tidymodels-community). If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/tune/issues). Either way, learn how to create and share a [reprex](https://rstd.io/reprex) (a minimal, reproducible example), to clearly communicate about your code. Check out further details on [contributing guidelines for tidymodels packages](https://www.tidymodels.org/contribute/) and [how to get help](https://www.tidymodels.org/help/).

>>>>

# infer R Package <img src="https://github.com/tidymodels/infer/blob/master/figs/infer_gnome.png?raw=true" align="right" width=250 />

@@

To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for the package is at <https://infer.tidymodels.org>.

@@

@@

For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://rstd.io/tidymodels-community). If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/infer/issues). Either way, learn how to create and share a [reprex](https://rstd.io/reprex) (a minimal, reproducible example), to clearly communicate about your code. Check out further details on [contributing guidelines for tidymodels packages](https://www.tidymodels.org/contribute/) and [how to get help](https://www.tidymodels.org/help/).
